### 2012-11-15 doc/progress_plan/report.tex
Fixed a couple of small errors
Rephrased section 1 and made things a bit less ambigious

Partridge is a web-based tool designed to assist in information processing and knowledge
acquisition within the domain of scientific research.

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
estimates that approximately 1.4 Million papers were published in the year 2006
alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available for free online\cite{Suber2012}) across
most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
providing researchers with an even larger volume of information to be
processed. As available information increases, relevant material becomes
progressively more difficult to find and the need for an automated information
retrieval tool more apparent. The problem is even more vital for General
Practitioners. Goldacre (2008:97) points out that ``there have been an
estimated 15 million medical academic articles published so far, and 5000
journals published every month... picking out what's relevant is a garganutan
task."\cite{goldacre2008bad}

Partridge aims to autonomously process as many scientific papers as possible to
facilitate researchers who would otherwise be required to manually read each
paper themselves. This should reduce the amount of information that the reader
is required to process themselves, thereby speeding up the research process.
Partridge will achieve this through the use of several existing techniques in
Natural Language Processing which are discussed below.

@@

There are already several tools that help researchers manage the vast library
of journals available on the internet. Search engines such as Google
({\url{http://www.google.com/}}), and social citation management tools such as
CiteULike ({\url{http://www.citeulike.org}}), do offer some assistance in
tracking down relevant information. However, these tools are often too general
or rely upon the user knowing exactly what keywords to use before carrying out
the search. These drawbacks are further discussed in Section
\ref{sec:prior_art} below.

To overcome the drawbacks of these existing systems, Partridge will make use of
several cutting edge Artificial Intelligence (AI) techniques in order to analyse and
process the papers in a more in depth way. AI is a very complex and field and
implementing the above features will be incredibly challenging. To help with
this, Partridge will build upon the system implemented by Liakata et al. for
classifying papers on a sentence-by-sentence basis\cite{citeulike:10444769} and
make use of Natural Language Toolkit for Python
\cite{bird2009natural}

@@

\appendix
\section{System Process Diagrams}
\label{sec:system_diagrams}

\appendix
\section{Project Timeline}
\label{sec:timeline}

\appendix
\section{Project Wiki}
\label{sec:wiki}

>>>>

This document describes the creation of Partridge, a new web-based tool
designed to assist in information processing and knowledge acquisition within
the domain of scientific research.

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
estimates that approximately 1.4 Million papers were published in the year 2006
alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available to readers for free online\cite{Suber2012}) across
most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
providing scientists and researchers with an even larger volume of information to be
processed. As available information increases, relevant material becomes
progressively more difficult to find and the need for an automated information
retrieval tool more apparent. The problem is even more vital for General
Practitioners. Goldacre (2008:97) points out that ``there have been an
estimated 15 million medical academic articles published so far, and 5000
journals published every month... picking out what's relevant is a gargantuan
task."\cite{goldacre2008bad}

Partridge's main objective is to provide reading recommendations and
information retrieval for scientists and researchers. This should reduce the
amount of extraneous information that users have to read for themselves by
helping them find information specific to their interests more quickly.
Partridge will achieve this through the use of several existing techniques in
Natural Language Processing which are discussed below.

@@

Search engines such as Google ({\url{http://www.google.com/}}), and social
citation management tools such as CiteULike ({\url{http://www.citeulike.org}}),
do offer some assistance in tracking down relevant information. However, these
tools are often too general or rely upon the user knowing exactly what keywords
to use before carrying out the search. These drawbacks are further discussed in 
Section \ref{sec:prior_art} below.

To overcome the drawbacks of these existing systems, Partridge will make use of
several cutting edge Artificial Intelligence (AI) techniques in order to analyse and
process the papers in a more in depth way. AI is a very complex and field and
implementing the above features will be incredibly challenging. To help with
this, Partridge will build upon the system implemented by Liakata et al. for
recognising hypotheses, methods, results, conclusions and a number of other
scientific concepts in scientific articles \cite{citeulike:10444769}. The
Natural Language Toolkit for Python will also be used to build models for
recognising different fields and topics, classifying results as positive or
negative and recognising different types of papers, from case studies to
methodology papers\cite{bird2009natural}.

@@

\section{System Process Diagrams}
\label{sec:system_diagrams}

\section{Project Timeline}
\label{sec:timeline}

\section{Project Wiki}
\label{sec:wiki}
